An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-03-30 empirics.Rnw
Revised paper

\newcolumntype{C}{>{\centering\arraybackslash}X}

<<echo=F>>=
library(dbframe)
library(xtable)

@@

fspace <- function(x) gsub(" ", "\\\\enskip", format(round(x, 1)))

printall <- function(mcdb,...) {
  d <- subset(select(mcdb, group.by = groups, 
                     sprintf(c("case isPower when 0 then 'size' else 'power' end as 'type'",
                               "R", "P", 
                               "100 * avg(pOld <= %f) as 'Pr[\\textsc{cw}]'",
                               "100 * avg(pNew1 <= %f) as 'Pr[new]'",
                               "100 * (avg(pOld <= %f and pNew1 > %f) + avg(pOld > %f and pNew1 <= %f)) as 'Pr[disagree]'"),
                             size, size, size, size)), select = -isPower)
  d$R <- fspace(d$R)
  d$P <- fspace(d$P)
  d[[4]] <- fspace(d[[4]])
  d[[5]] <- fspace(d[[5]])
  d[[6]] <- fspace(d[[6]])
  d$R[duplicated(subset(d, select = c(type, R)))] <- NA
  d$type[duplicated(d$type)] <- NA
  printbooktabs(d, include.rownames = FALSE, digits = c(0,0,0,0,1,1,1), 
                align = c("l","X","C","C","C","C","C"), 
                sanitize.text.function = function(x) x,
                tabular.environment = "tabularx")
  invisible(d)
}
@

This is the empirical section

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS
% LocalWords:  ClM

>>>>

\newcolumntype{C}{>{\centering\arraybackslash}X}
\SweaveOpts{prefix.string=floats/empirics}
\SweaveOpts{split=TRUE}

<<echo=F>>=
library(xtable)
library(Hmisc)
load("empirics.RData")
attach(results)

@@

fspace <- function(x, rnd=1) gsub("-", "--", gsub(" ", "\\\\enskip", format(round(x, rnd))))
@

This section demonstrates the use of the statistics introduced earlier
in the paper by revisiting \citepos{GoW:08} study of excess stock
returns.  Goyal and Welch argue that many variables thought to predict
excess returns (measured as the difference between the yearly log
return of the S\&P 500 index and the T-bill interest rate) on the
basis of in-sample evidence fail to do so out-of-sample.  To show
this, Goyal and Welch look at the forecasting performance of models
using a lag of the variable of interest, and show that these models do
not significantly outperform the excess return's recursive sample mean.

Here, I conduct the same analysis,, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\]
where $\alpha_{0}$ and $\alpha_{1}$ are estimated by \ols\ using a
10-year window.  The predictors used are listed in the ``predictor''
column of Table~\ref{tab:em1} \citep[see][for a detailed description
of the variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window is of
length 10.

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-10\% critical value
(\Sexpr{round(qnorm(.9),2)}) and the critical value estimated by the
procedure of Theorem~\ref{res:2}
(\Sexpr{round(sqrt(crit),2)}).\footnote{The bootstrap uses 999
  replications, and we use the i.i.d. bootstrap proposed in
  Part~\ref{it:1} of Theorem~\ref{res:2}.}  Three predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.  But none are significant after accounting for
data-snooping, which highlights the importance of these methods.  The
median forecast is significant using conventional critical values as
well, but not the corrected values.

\begin{table}[tb!]
  \centering
<<table, echo=F, results=tex>>=
k <- length(tstats)/2 - 1
d <- data.frame(notes = c("Original", rep("", k-1), "CT correction", rep("", k-1), "Combination", ""),
                predictor = names(tstats),
                tstat = fspace(tstats, 2),
                naive = ifelse(tstats > qnorm(.9), "sig.", ""),
                smart  = ifelse(tstats > crit, "sig.", ""),
                row.names = 1:(2*k + 2))
colnames(d)[1] <- " "
colnames(d)[3] <- "value"
colnames(d)[4] <- "naive"
colnames(d)[5] <- "corrected"

d$predictor <- gsub("\\.mu", "", d$predictor)
d$predictor <- gsub("\\.CT", "", d$predictor)
d$predictor <- gsub("\\.", " ", d$predictor)
d$predictor <- capitalize(d$predictor)

printbooktabs(d, sanitize.text.function = function(x) x, include.rownames = FALSE,
              align = c("l", "l", "l", rep("C", 3)), tabular.environment = "tabularx")
@ 
\caption{Results from \oos\ comparison of equity premium prediction
  models; the benchmark is the recursive sample mean of the equity
  premium and each alternative model is a constant and single lag of
  the variable listed in the ``predictor'' column.  The dataset begins
  in 1927 and ends in 2009 and is annual data. The ``value'' column
  lists the value of this paper's \oos\ statistic, the ``naive''
  column indicates whether the statistic is significant at standard
  critical values, and the ``corrected'' column indicates significance
  using the critical values proposed in Theorem~\ref{res:2} that
  account for the number of models.  See Section~\ref{sec:3} for details.}
\label{tab:em1}
\end{table}

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS Hmisc
% LocalWords:  ClM empirics RData gsub tabularx textwidth fspace rnd enskip GoW
% LocalWords:  Goyal Welch return's CaT qnorm crit tstats tstat ifelse sig sqrt
% LocalWords:  colnames

### 2012-03-30 mc.Rnw
Revised paper

\newcolumntype{C}{>{\centering\arraybackslash}X}

@@

I'll also conduct two brief Monte Carlo experiments to demonstrate
that the modified version of \citepos{ClW:07} statistic performs
similarly to their original test.\footnote{All of these simulations
  were programmed in R \citep{R:2-13-0} and use the \textsc{MASS}
  \citep[ver. 7.3-12]{VeR:02}, xtable \citep[ver. 1.5-6]{Dah:09},
  dbframe \citep[ver. 0.1.1]{Cal:10b}, and \textsc{oos}
  \citep[ver. 0.01]{Cal:11b} packages.}  We'll use both of the \dgp s
they consider.  For the first, we have
\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
  y_t &= 0.5 + \gamma^{*} z_{t-1} + e_t &
  \gamma^{*} &=
  \begin{cases}
    0 & \text{size simulations} \\
    0.35 & \text{power simulations}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
\end{align}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We use both \poscw\ original statistic and our new
statistic to test the null that the benchmark model's innovation is an
\mds.\footnote{\citet{ClW:07} report the performance of the tests
  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
  based on the naive Gaussian statistic.}

@@

Table~\ref{tab:mc1} presents the simulation results
for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
all of the parameter values, our proposed new statistic has slightly
lower rejection probability than \citepos{ClW:07}.  For both \dgp s
the statistics are slightly undersized.  In~\eqref{eq:dgp1}, this
translates to relatively low power and the power difference between
the two statistics may be noticeable.  In~\eqref{eq:dgp2}, though, the
evidence against the benchmark is strong enough under the alternative
that the tests reject almost all of the time.  In that setting, the
lower power of our new test is essentially irrelevant.

@@

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS gsub
% LocalWords:  ClM tabularx textwidth fspace enskip

>>>>

\newcolumntype{C}{>{\centering\arraybackslash}X}
\SweaveOpts{prefix.string=floats/mc}
\SweaveOpts{split=TRUE}

@@

I'll conduct two brief Monte Carlo experiments to demonstrate that the
modified version of \citepos{ClW:07} statistic performs similarly to
their original test.\footnote{All of these simulations were programmed
  in R \citep{R:2-13-0} and use the \textsc{MASS} \citep{VeR:02},
  xtable \citep{Dah:09}, dbframe \citep{Cal:10b}, and \textsc{oos}
  \citep{Cal:11b} packages.  Version information is listed in the
  bibliography.}  We'll use both of the \dgp s they consider.  For the
first, we have
\begin{align}\label{eq:dgp1}\tag{\dgp\ 1}
  y_t &= 0.5 + \gamma^{*} z_{t-1} + e_t &
  \gamma^{*} &=
  \begin{cases}
    0 & \text{size simulations} \\
    0.35 & \text{power simulations}
  \end{cases}\\\nonumber
  z_t &= 0.15 + 0.95 z_{t-1} + v_t &
  (e_t, v_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
\end{align}
Both models are estimated by \ols. The benchmark model regresses $y_t$
on a constant, and the alternative regresses $y_t$ on a constant and
$z_{t-1}$.  We use both \poscw\ original statistic and the new
statistic to test the null that the benchmark model's innovation is an
\mds.\footnote{\citet{ClW:07} report the performance of the tests
  proposed by \citet{CCS:01} and \citet{ClM:05} as well, and of tests
  based on the naive Gaussian statistic.}

@@

Table~\ref{tab:mc1} presents the simulation results
for~(\ref{eq:dgp1}) and Table~\ref{tab:mc2} for~(\ref{eq:dgp2}).  For
all of the parameter values, the proposed new statistic has similar
rejection probability to \citepos{ClW:07}.  Clark and West's test is
slightly more undersized than the new test, but has a little higher
power under the alternative.  Moreover, the statistics give different
results in less than 10\% of the simulations for most parametrizations
of the \dgp s.  In general, the statistics perform similarly well.

@@

%%% Local Variables:
%%% TeX-master: "Paper"
%%% End:
% LocalWords:  dbframe xtable mcdata dgp printbooktabs hline pos nrow toprule
% LocalWords:  midrule bottomrule printall mcdb dsize isPower sprintf pOld pNew
% LocalWords:  dpower qs dadj dfapply rownames tb tex oos eqref eq mc ClW dgp's
% LocalWords:  citepos nonumber sim iid Bigg binom pmatrix ols poscw CCS gsub
% LocalWords:  ClM tabularx textwidth fspace enskip VeR Dah
